Semi-Supervised Factored Logistic Regression for High-Dimensional Neuroimaging Data

### 2015-06-05 paper_nips/paper.tex
minor
standard deviation

\paragraph{Layer combination.}
Importantly, the optimization problem of the linear autoencoder
and the factored logistic regression
are linked on two levels. First, their transformation matrices mapping from
input to the latent space are tied
\begin{eqnarray}
  \mathbf{V_0} = \mathbf{W_0}.
\end{eqnarray}
We thus search for a compression of the 79,941 voxel values into $n$ latent
components that represent a latent code optimized for both
rest and task activity data.
Second, the objectives of the autoencoder and the factored
logistic regression are interpolated in the common loss function
% XXX Michael: In resolving conflict I opted for my change. Feel free to revert if that was intended.
\begin{equation}
{\mathcal{L}}(\theta, \lambda) = \lambda {\mathcal{L_{LR}}}
+ (1-\lambda)\frac{1}{N_{X_{rest}}} {\mathcal{L_{AE}}} + \Omega(\theta).
  \label{eq:loss_equ}
\end{equation}

@@

\paragraph{Optimization.}
The common objective was optimized
by gradient descent in the SSFLogReg parameters.
%^
The required gradients were obtained by using the chain rule to
backpropagate error derivatives.
We chose the \textit{rmsprop} solver \cite{rmsprop},
a refinement of stochastic gradient descent.
\textit{Rmsprop} dictates an adaptive learning rate
for each model parameter by
scaled gradients from a running average.
The batch size was set to $100$
(much expected redundancy in $X_{rest}$ and $X_{task}$),
matrix parameters were initalized by Gaussian random values multiplied
by $0.004$ (i.e., gain), and
bias parameters were initalized to $0$.

>>>>

\paragraph{Layer combination.}
Importantly, the optimization problem of the linear autoencoder
and the factored logistic regression
are linked on two levels. First, their transformation matrices mapping from
input to the latent space are tied, i.e.
\begin{eqnarray}
  \mathbf{V_0} = \mathbf{W_0}.
\end{eqnarray}
We thus search for a compression of the 79,941 voxel values into $n$ latent
components that represent a latent code optimized for both
rest and task activity data.
Second, the objectives of the autoencoder and the factored
logistic regression are interpolated in the common loss function
% XXX Michael: In resolving conflict I opted for my change. Feel free to revert if that was intended.
\begin{equation}
{\mathcal{L}}(\theta, \lambda) = \lambda {\mathcal{L_{LR}}}
+ (1-\lambda)\frac{1}{N_{X_{rest}}} {\mathcal{L_{AE}}} + \Omega(\theta).
  \label{eq:loss_equ}
\end{equation}

@@

\paragraph{Optimization.}
The common objective was optimized
by gradient descent in the SSFLogReg parameters.
%^
The required gradients were obtained by using the chain rule to
backpropagate error derivatives.
We chose the \textit{rmsprop} solver \cite{rmsprop},
a refinement of stochastic gradient descent.
\textit{Rmsprop} dictates an adaptive learning rate
for each model parameter by
scaled gradients from a running average.
The batch size was set to $100$
(much expected redundancy in $X_{rest}$ and $X_{task}$),
matrix parameters were initalized by Gaussian random values with
standard deviation $0.004$ (i.e., gain), and
bias parameters were initalized to $0$.
